Integrated farming and global warming mitigation in Brazil

### 2022-09-20 manuscript/manuscript.qmd
Add text in the methods.

@@

@@

>>>>

The overview of ICLF systems in Brazil will be performed by analyzing published research and web surveys with experts.

@@

The literature review will be performed over published research from two sources, Scopus and Embrapa. It will have a very general approach, in which any research analyzing any aspect of ICLF will be screened. The strings that will be used to search research are the following:

*   Scopus: TITLE-ABS-KEY(iclf OR iclfs OR crop-livestock-forestry OR crop-livestock-forest OR agrosilvipastoral OR ilpf OR lavoura-pecuária-floresta OR agrosilvipastoril) AND PUBYEAR > 1999

* Embrapa: ((ICLF) OR (iclfs) OR (crop-livestock-forestry) OR (crop-livestock-forest) OR (agrosilvipastoral) OR (ilpf) OR (lavoura-pecuária-floresta) OR (agrosilvipastoril)) AND (ano-publicacao:[2000 TO *]) AND (tipo-material-sigla:"PC" OR tipo-material-sigla:"AP" OR tipo-material-sigla:"NC" OR tipo-material-sigla:"RT") AND (idioma:"Inglês" OR idioma:"Português")

The data and information extract from selected research will be diverse, and will be organized in 11 relational tables. The tables will cover general information about the research document and characteristics of the experiment, as also data about the system management, soil properties, productivity, growth, emissions, and radiation. All tables will be described by metadata files.

An important assumption of the review is that the ICLF experiments are representative of the ICLF being implemented by farmers in Brazil.

@@

The experts survey will be performed by a web application where the participants will be able to interact with a questionnaire to provide information about ICLF systems.

The nature of the survey is semi-structured, with closed and open questions. The participants will have the option to avoid answering any question.

The participants desired profile is of researchers or technicians with any experience with ICLF systems. A minimum of 50 participants is expected.

The objective of the survey is to gather information that are not available in the literature, as also to provide expected scenarios to the ICLF expansion in the future.

All answers will be stored in tables for posterior analysis. Each question will be represented by a column, and each participant will be represented as a row (one observation for each question).

The web application will be deployed in a personal website, where the participants will receive the link of the survey, along with a token that will be used to submit the answers.
